---
title: "simpleRegress"
author: "Sara Whitaker"
date: "November 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,interval = "prediction")
```

## Introduction 

We are comparing the variables CHEST and the variable NECK to see which variable is better at determining length 

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK 

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Neck as a variable for determining a bear's length and adjusted R square of 0.7476

The scatter plot shows as the neck size increases, so does length. Thus, neck size is the better predictor to determine length .

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```

## Numerical Summary

```{r}
cor(bears$LENGTH,bears$NECK)
```

## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```


This Scatter plot shows that as the CHEST size goes up, so does length. Thus, CHEST size is the better predictor to determine the length of a bear. 

```{r}
cor(bears$LENGTH,bears$CHEST)
```
## Conclusion 

Chest is the better predictor of length than neck is because the adjusted r-squared test of the fit for CHEST was larger than the adjusted r squared of the fit for NECK. 
